### 2012-04-12 trunk/ijcis-pos-model/sources/preliminaries.tex
new modifications

\subsection{\label{subsec:fuzzy-numbers}Fuzzy Numbers and Fuzzy Intervals}
Among others, Dubois and Prade~\cite{Dubois1983} use fuzzy sets \cite{Zadeh1965} to define a \emph{fuzzy interval}:
\begin{definition}
A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$, on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\mu_{M} :  \mathbb{R} \rightarrow \left[0,1\right] \nonumber \\ 
\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:\\
\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R} :  \mu_M(m)=1 
\end{eqnarray}
\end{definition}
If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}. In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number.

A simple form of the membership function of a fuzzy interval is a trapezoidal function. It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. Four reel values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as $\left[\alpha, \beta, \gamma, \delta\right]$. The corresponding membership function definition for this $\mu_T$ is then given by:

@@

%\def\JPicScale{0.5}
%\begin{figure}[h!]
%  \centering
%  \input{./graphs/trapezoidal.tex}
%  \caption{Trapezoidal membership function}
%  \label{fig:trapezoidal}
%\end{figure}

@@

Now, e.g., to check if crisp interval $I = \left[j, k\right]$ is included in $\left[X, Y\right]$, 2 ill-known constraints are constructed:

@@

\begin{align}
\label{eq:interval-pos}
\Pos(I\text{ satisfies }C_1\ and\ C_2) & =\\
\nonumber
\min_{a \in I}\left(\sup_{a \geq w}\pi_{X}(w),\sup_{a \leq v}\pi_{Y}(v)\right)\\
\label{eq:interval-nec}
\Nec(I\text{ satisfies }C_1\ and\ C_2) & =\\
\nonumber
\min_{a \in I}\left(\inf_{a < w} 1-\pi_{X}(w),\inf_{a > v} 1-\pi_{Y}(v)\right).
\end{align}

Sometimes, an ill-known value might be specified by some boolean combination of ill-known constraints. This allow to define ill-known values by means of relationships with respect to other ill-known points.

@@

\begin{definition}
Consider a universe $U$, an n-ary vector $\mathbf{C}$ of ill-known constraints over the variables $Z_1, \ldots, Z_n$ and a Boolean function $\bool:\mathbb{B}^{n}\rightarrow\mathbb{B}$. The uncertainty about the evaluation of an ill-known value $X$ is given by:
\begin{align}
\label{eq:ill-known-value-def-by-const-unc}
X \in \Pow(U):\pi_{X}=\widetilde{\bool}\Big(\pi_{C_1(Z_1)},\ldots,\pi_{C_n(Z_n)}\Big)
\end{align} 
\end{definition}

\begin{example}
Consider the ill-known values $X = \left[12, 2, 2\right]$ and $Y = \left[18, 2, 1 \right]$. The ill-known value $Z$ is defined using ill-known constraints w.r.t. the ill-known values $X$ and $Y$:
\begin{align}
\nonumber
Z \triangleq \left \lbrace C_1\left(>,X\right) \wedge C_2(\leq,Y) \right \rbrace
\end{align}
$Z$ is a fuzzy interval defined by a trapezoidal shape given by $\left[12,\ 14,\ 18,\ 19 \right]$
Figure \ref{fig:example-ill-known-by-const} illustrates the relations among the variables $X$, $Y$ and $Z$.
\end{example}

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/ill-known-by-constraints.pdf}
\label{fig:example-ill-known-by-const}
}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{Ill-known values $X$ and $Y$. The grey area represents the ill-known value $Z$ defined by two ill-known constraints.}
\vspace*{13pt}

>>>>

\subsection{\label{subsec:fuzzy-numbers}Fuzzy Numbers and Fuzzy Intervals}
Among others, Dubois and Prade~\cite{Dubois1983} use fuzzy sets \cite{Zadeh1965} to define a \emph{fuzzy interval}:
\begin{definition}
A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$, on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\mu_{M} :  \mathbb{R} \rightarrow \left[0,1\right] \nonumber \\ 
\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:\\
\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R} :  \mu_M(m)=1 
\end{eqnarray}
\end{definition}

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=0.25]{./graphs/triangular.pdf}

}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:triangular-dist}Trapezoidal membership function.}
%  \label{fig:fuzzy-validity-period}
\vspace*{13pt}

If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}. In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number (Figure \ref{fig:triangular-dist}).

A simple form of the membership function of a fuzzy interval is a trapezoidal function (Figure \ref{fig:trapezoidal-dist}. It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. Four reel values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as $\left[\alpha, \beta, \gamma, \delta\right]$. The corresponding membership function definition for this $\mu_T$ is then given by:

@@

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=0.25]{./graphs/trapezoidalDistribution.pdf}

}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:trapezoidal-dist}Trapezoidal membership function.}
%  \label{fig:fuzzy-validity-period}
\vspace*{13pt}
%\def\JPicScale{0.5}
%\begin{figure}[h!]
%  \centering
%  \input{./graphs/trapezoidal.tex}
%  \caption{Trapezoidal membership function}
%  \label{fig:trapezoidal}
%\end{figure}

@@

\begin{example}
Consider that we want to check if crisp interval $I = \left[j, k\right]$ is included in $\left[X, Y\right]$, 2 ill-known constraints are constructed:

@@

\begin{align}
\label{eq:interval-pos}
\Pos(I\text{ satisfies }C_1\ and\ C_2) & =\\
\nonumber
\min_{a \in I}\left(\sup_{a \geq w}\pi_{X}(w),\sup_{a \leq v}\pi_{Y}(v)\right)\\
\label{eq:interval-nec}
\Nec(I\text{ satisfies }C_1\ and\ C_2) & =\\
\nonumber
\min_{a \in I}\left(\inf_{a < w} 1-\pi_{X}(w),\inf_{a > v} 1-\pi_{Y}(v)\right).
\end{align}
\end{example}

There is a special boolean combination of constraints that is of particular interest:
\begin{definition}
\emph{Convex combination of ill-known constraints}. Consider the $C_1$ and $C_2$ two ill-known constraints. A convex combination of the constraints is given by:
\begin{align}
\label{eq:convex-combination}
CC \triangleq \left \lbrace C_1 \wedge C_2 \right \rbrace
\end{align}
In a more general way, it is possible to define the convex combination of an n-ary vector  $\mathbf{C}$ of constraints:
\begin{align}
\label{eq:nary-convex-combination}
CC \triangleq \left \lbrace C_1 \wedge \ldots \wedge C_n \right \rbrace
\end{align}
\end{definition}

\begin{theorem}
\label{th:convex-combination-ill-known-constraints}
Consider the convex combination $CC$ of any n-ary vector $\mathbf{C} = \left \lbrace C_{1_{Z_1}}, \ldots, C_{n_{Z_n}} \right \rbrace$ of constraints over the ill-known variables $Z_1, \ldots, Z_n$. Then, if $\pi_{C_1(Z_1)}, \ldots, \pi_{C_n(Z_n)}$ are convex, then  $\pi_{CC}$ is also convex.
\end{theorem}

\begin{proof}
Let $CC \triangleq \left \lbrace C_{1_{Z_1}}, \ldots, C_{n_{Z_n}}  \right \rbrace$. Then:
\begin{align}
\label{eq:proof-convex1}
\pi_{CC} \left( \lambda x_1 + \left( 1 - \lambda \right)x_2 \right) = \\
\min  \big( \pi_{C_1(Z_1)}\left( \lambda x_1 + \left( 1 - \lambda \right)x_2 \right), \ldots,\\
   \pi_{C_n(Z_n)}\left( \lambda x_1 + \left( 1 - \lambda \right)x_2 \right)  \big)
\end{align}
Since $\pi_{C_1(Z_1)}, \ldots, \pi_{C_n(Z_n)}$ are convex:
\begin{align}
\label{eq:proof-convex2}
\pi_{C_1(Z_1)} \left(\lambda x_1 + \left( 1 - \lambda \right)x_2  \right) \geqq \\
\nonumber
\min \big(\pi_{C_1(Z_1)} \left( x_1 \right),\pi_{C_1(Z_1)} \left( x_2 \right)  \big)\\
\nonumber
\vdots \\
\nonumber
\pi_{C_n(Z_n)} \left(\lambda x_1 + \left( 1 - \lambda \right)x_2  \right) \geqq \\
\nonumber
\min \big(\pi_{C_n(Z_n)} \left( x_1 \right),\pi_{C_n(Z_n)} \left( x_2 \right) \big) 
\end{align}
Then, by using equation \eqref{eq:proof-convex1}:
\begin{align}
\label{eq:proof-convex3}
\pi_{CC} \left( \lambda x_1 + \left( 1 - \lambda \right)x_2 \right) \geqq  \\
\nonumber
\min \big( \min \left(\pi_{C_1(Z_1)} \left( x_1 \right),\pi_{C_1(Z_1)} \left( x_2 \right) \right),\\
\nonumber
\ldots, \min \left(\pi_{C_n(Z_n)} \left( x_1 \right),\pi_{C_n(Z_n)} \left( x_2 \right) \right) \big)
\end{align}
Which is equivalent to the following:
\begin{align}
\label{eq:proof-convex4}
\pi_{CC} \left( \lambda x_1 + \left( 1 - \lambda \right)x_2 \right) \geqq  \\
\nonumber
\min \big( \min \left(\pi_{C_1(Z_1)} \left( x_1 \right), \ldots, \pi_{C_n(Z_n)} \left( x_1 \right) \right),\\
\nonumber
\ldots, \min \left(\pi_{C_1(Z_1)} \left( x_2 \right), \ldots, \pi_{C_n(Z_n)} \left( x_2 \right) \right) \big)
\end{align}
Finally we obtain:
\begin{align}
\label{eq:proof-convex5}
\pi_{CC} \left( \lambda x_1 + \left( 1 - \lambda \right)x_2 \right) \geqq  \\
\nonumber
\min \big(\pi_{CC} \left( x_1 \right), \pi_{CC} \left( x_2 \right) \big)
\end{align}
\end{proof}

Sometimes, an ill-known value might be specified by a convex combination of ill-known constraints. This allow to define ill-known values by means of relationships with respect to other ill-known points.

@@

\begin{definition}
Consider a universe $U$, $X$ an ill-known value and $CC \triangleq \left \lbrace C_{1_{Z_1}}, \ldots, C_{n_{Z_n}}  \right \rbrace$ a convex combination of ill-known constraints over the variables $Z_1, \ldots, Z_n$. The value $X$ is defined by means of the convex combination:
\begin{align}
\label{eq:ill-known-value-by-convex-constraints}
X \triangleq CC 
\end{align}

The uncertainty about the evaluation of an ill-known value $X$ is given by:
\begin{align}
\label{eq:ill-known-value-def-by-const-unc}
X \in \Pow(U):\pi_{X}=\pi_{CC}
\end{align} 
Note that $\pi_{X}$ is convex since $\pi_{CC}$ is convex as demostrated in theorem \ref{th:convex-combination-ill-known-constraints}.
\end{definition}

\begin{example}
Consider the ill-known values $X = \left[12, 2, 2\right]$ and $Y = \left[18, 2, 1 \right]$. The ill-known value $Z$ is defined using the convex combination $CC$ of constraints $C_1$ and $C_2$:
\begin{align}
\nonumber
CC \triangleq \left \lbrace C_1\left(>,X\right) \wedge C_2(\leq,Y) \right \rbrace \\
\nonumber
Z \triangleq CC
\end{align}
$Z$ is a fuzzy interval defined by a trapezoidal shape given by $\left[12,\ 14,\ 18,\ 19 \right]$
Figure \ref{fig:example-ill-known-by-const} illustrates the relations among the variables $X$, $Y$ and $Z$.
\end{example}

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/ill-known-by-constraints.pdf}
\label{fig:example-ill-known-by-const}
}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{Ill-known values $X$ and $Y$. The grey area represents the ill-known value $Z$ defined by the convex combination of the two ill-known constraints $C_1$ and $C_2$.}
\vspace*{13pt}
